\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2023-01-06 src/tex/ms.tex
Finished first draft of discussion

@@

In this paper, we have primarily focussed on the IMRPhenom family of waveforms as their closed form expression is perfectly suited for implementation in \jax.
Two other waveform families are commonly used in GW data analysis: the effective-one-body (EOB) and numerical relativity surrogate (NRSurrogate). 
Some progress has been made towards the construction of a differentiable NRsurrogate, currently it seems difficult to implement EOB waveforms in \jax.
In particular, the evolution of the Hamiltonian required to evaluate an EOB waveform is both inherently slow to differentiate and difficult to implement in \jax which requires fixed length arrays for its JIT compilation.
Since EOB waveforms are often regarded as the state-of-the-art, more work is required to see if a fast, differentiable implementation is possible.

\te{End on a final good thing?}

>>>>

In this paper, we have primarily focussed on the IMRPhenom family of waveforms as their closed form expression is perfectly suited for implementation in \jax.
Two other waveform families are commonly used in GW data analysis: the effective-one-body (EOB) and numerical relativity surrogate (NRSurrogate). 
Some progress has been made towards the construction of a differentiable NRsurrogate, but currently it seems difficult to implement EOB waveforms in \jax.
In particular, the evolution of the Hamiltonian required to evaluate an EOB waveform is both inherently slow to differentiate and difficult to implement in \jax which requires fixed length arrays for its JIT compilation.
Since EOB waveforms are often regarded as the state-of-the-art, more work is required to see if a fast, differentiable implementation is possible.

@@
